---
header-includes:
  - \usepackage{multirow}
  - \usepackage{float}
output: pdf_document
params:
  send_date: temp
  fname: temp
  lname: temp
  donation: temp
  date: temp
  ty: temp
  directory: temp
---
```{r, echo=FALSE, fig.align='center'}
include_graphics(params$directory)
```


`r params$send_date`  
\hfill\break  
**Subject: Thank You for Your Donation and Welcome to the GWRFC Blazer Club**  
\hfill\break
Dear `r params$fname` `r params$lname`,  
  
Thank you so much for contributing to the success of the George Washington Rugby Football
Club and the Club’s Alumni Association. The GWRFC Alumni Association, Inc. (EIN
#82-1151809) is a Virginia nonstock corporation that is eligible to receive tax exempt
contributions under section 501(c)(3) of the Internal Revenue Code. The Club and Association
are able to continue growing, purchase practice and game equipment, and celebrate the game
we love thanks primarily to generous donations like yours.  

We want to thank you especially for your long-term support to both the Club and the Alumni Organization
by inducting you into the GWRFC Blazer Club and presenting you with a custom blazer.

Find below the details of your donations in `r params$ty`. We look forward to sharing specifics on the
impacts of your donation in the weekly newsletter and at future Alumni Association events.
Please do not hesitate to reach out with feedback on the Club, the Association, or with general
questions.  
  
  
```{r, echo=FALSE}
library(knitr)
library(kableExtra)
library(magrittr)

df <- data.frame(Donor = paste(params$fname, params$lname, sep = " "),
                 Donation = paste0("$", params$donation),
                 Date = params$date)

df %>% kbl(format = 'latex', align = 'c') %>% kable_styling(position = "center", latex_options = "HOLD_position")
```
This letter is also intended to serve as contemporaneous written acknowledgment of your donation to comply with 26 U.S. Code § 170(f)(8)(a).
Additionally, the GWRFC Alumni Association has provided a jacket worth $200 to you. Consequently, the amount of your $`r params$donation` 
donation that is deductible for federal income tax purposes is limited to the excess of any money contributed over the value of 
goods provided by the GWRFC Alumni Association. Once again, thank you for your donation and continued support to the George Washington
Rugby Football Club and the Club's Alumni Association.  
\hfill\break
Best regards,  
  
Trevor Ceniviva, President  
Adam Lurie, Vice President  
John Kelley, Treasurer  
Joe Hancuch, Secretary  
Mike Ferrier, Alumni Liaison  
